Robustly decorrelating errors with mixed quantum gates

### 2020-05-06 decorrelation/mixed_unitaries.tex
incorrect figure reference on page 7
final changes to text from anthony, regeenrated text

 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively. Using these probabilities and pulse amplitudes we have plotted the corresponding error generators in Fig. \ref{ptms}. $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear suppression of these off-diagonal elements.
\begin{figure}
\includegraphics[scale=.5]{experimental-ptm.png}
\label{ptms}
\caption{Hinton diagrams representing the error generators for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e) a Pauli-exact MQG. White boxes correspond to positive values, black  boxes correspond to negative values, and the size of the box corresponds to the magnitude of each entry. The four constituent pulses can be seen to have coherent errors from the off-diagonal components of their error generators. The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.}   
\end{figure}

@@

\begin{figure}
\includegraphics[width=\linewidth]{sparisity-versus-parameter_kcy.png}
\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$. Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=0.0001$, $\lambda_2=0.00025$ and $\lambda_3=0.0005$. As the parameter is increased from zero, the number of controls with low probability increases (seen on the plot as the probability mass moving to the left). For $\lambda_3$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
\label{fig:sparsity}
\end{figure}
To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls. Using the results from in Section \ref{sec:sparsity} we generated MQGs that sample from only 10 of these controls. Fig.~\ref{fig:sparsity} shows solutions to Eq.~\eqref{eq:minimization_sparsity} for different choices of  $\lambda$. As $\lambda$ increases, the optimal solution contains fewer controls with large support.

@@

Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other control routines such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.

>>>>

 These gates are then used as in Sec.~\ref{sub:off_diagonals} to construct a Pauli-exact MQG, which samples from the miscalibrated waveforms with probabilities $P\in \{0.307, 0.283, 0.211, 0.199\}$ respectively. Using these probabilities and pulse amplitudes we have plotted the corresponding error generators in Fig.~\ref{fig:ptms}. $\mathsf{Pulse1}$ through $\mathsf{Pulse4}$ show clear coherent errors as off-diagonal elements while the MQG exhibits a clear suppression of these off-diagonal elements.
\begin{figure}
\includegraphics[scale=.5]{experimental-ptm.png}
\caption{Hinton diagrams representing the error generators for a) $\mathsf{Pulse1}$, b) $\mathsf{Pulse2}$, c) $\mathsf{Pulse3}$, d) $\mathsf{Pulse4}$ and e) a Pauli-exact MQG. White boxes correspond to positive values, black  boxes correspond to negative values, and the size of the box corresponds to the magnitude of each entry. The four constituent pulses can be seen to have coherent errors from the off-diagonal components of their error generators. The Pauli-exact MQG has been constructed to have minimal coherent error and therefore has only diagonal elements.}   
\label{fig:ptms}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{sparisity-versus-parameter_kcy.png}
\caption{Sparsity of MQGs as a function of the sparisty parameter $\lambda$. Numerical values of $\lambda_i$ are: $\lambda_0=0$, $\lambda_1=0.0001$, $\lambda_2=0.00025$ and $\lambda_3=0.0005$. As the parameter is increased from zero, the number of controls with low probability increases (seen on the plot as the probability mass moving to the left). For $\lambda_3$ virtually all of the 750 controls have vanishingly small probability, allowing for the restriction of the MQG to a small number of controls.}
\label{fig:sparsity}
\end{figure}
To generate the initial controls, we use the GRAPE algorithm\cite{Khaneja2005} with N=25 steps and total evolution time of $\pi$ to generate 750 candidate controls. Using the results from in Section \ref{sec:sparsity} we generated MQGs that sample from only 10 of these controls. Fig.~\ref{fig:sparsity} shows solutions to Eq.~\eqref{eq:minimization_sparsity} for different choices of  $\lambda$. As $\lambda$ increases, most of the weights in the optimal solution become smaller, resulting in a sparser MQG.

@@

Future directions for this work include demonstrating the routine experimentally on a two-qubit gate, moving the random gate selection from a pre-compilation step to runtime logic onboard the control electronics, investigating other control generation algorithms such as CRAB \cite{Caneva2011} and GOAT\cite{Machnes2018}, and using more sophisticated benchmarking routines such as GST\cite{BlumeKohout2017} to quantitatively investigate the performance of our method.
